% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Experience}{}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
\researchexperience
    {Present}   {Massachusetts Institute of Technology, USA}{}{}
    {May 2020} {\textit{Research Intern (Senior Thesis) | Advisor:  \href{http://probcomp.csail.mit.edu/principal-investigator/}{Prof. Vikash Mansinghka}, Principal Investigator - Probabilistic Computing Project}
    \begin{itemize}
        \item Contributed to Gen.jl - MIT's probabilistic programming language.
        \item Built a BNF grammar based transpiler to convert Stan programs to Gen using Julia's meta-programming capabilities.
        \item Conducted a large scale benchmarking study of various MCMC based inference algorithms.
    \end{itemize}}
  \emptySeparator
 \researchexperience
    {September 2020}   {Julia Gaussian Processes}{}{}
    {June 2020} {\textit{Google Summer Of Code 2020 | Mentor: \href{http://mlg.eng.cam.ac.uk/hong/}{Dr. Hong Ge}, Senior Researcher, \href{http://mlg.eng.cam.ac.uk/}{MLG - University of Cambridge}}
    \begin{itemize}
        \item Contributed to \href{https://github.com/JuliaGaussianProcesses/}{JuliaGaussianProcesses} - a native Julia Gaussian Processes(GPs) modelling ecosystem.
        \item Implemented several GP related exact and approximate inference algorithms.
        \item Helped design and implement data abstractions and kernels for multi-output kernels.
        \item Adopted continuous integration and automatic documentation processes through TravisCI.
    \end{itemize}        
    }
  \emptySeparator
    \researchexperience
    {December 2019}   {APPCAIR Lab, BITS Pilani}{}{}
    {February 2019} {\textit{Undergraduate Researcher | Advisors: \href{https://scholar.google.com.au/citations?user=zpNTeogAAAAJ}{Prof Ashwin Srinivasan}, Professor; \href{https://scholar.google.co.in/citations?user=IJjnjZIAAAAJ}{Ramya Hebbalaguppe}, Scientist, \href{https://www.tcs.com/tcs-research}{TCS Research}}\\
    Worked on KL divergence based compression techniques for deep neural networks in collaboration with \href{https://www.tcs.com/tcs-research}{TCS Research}. This work has been accepted at ESANN'20.
    }
  \emptySeparator
   \researchexperience
    {July 2019}   {INRIA - French Institute for Research in Computer Science and Automation, France}{}{}
    {June 2019} {\textit{Summer Research Intern | Advisors: \href{https://www.julyanarbel.com}{Dr. Julyan Arbel}, Researcher, \href{https://team.inria.fr/mistis/}{MISTIS Team}}
        \begin{itemize}
            \item Investigated asymptotic consistency of posteriors of Bayesian Neural Networks(BNNs). 
            \item Analysed the sensitivity of the posterior uncertainty quantification on priors of the BNNs.
            \item Studied and visualised heavy tailed nature of the units of a BNNs.
            \item Worked extensively with several probabilistic programming languages(PPLs) including PyMC3,
        \end{itemize}
    }
  \emptySeparator
    
   \researchexperience
    {August 2017}   {Mozilla Foundation (Bugzilla)}{}{Remote}
    {May 2017} {\textit{Google Summer of Code 2017 | Mentor: \href{https://www.linkedin.com/in/dylanwh}{Dylan Hardison}}\\
    Revamped the existing bug filing interface (enter\_bug.cgi) into a single page reducing the multi-hop db access and unnecessary template rendering. This enhanced the speed and performance in bug filing.
                    }
  
\end{experiences}
\vspace{-4mm}
